Untitled

### 2017-05-30 PlotwithLeaflet.Rmd
Simplify polygon
Used the rmapshaper package to simplify the polygons which means they take up less space than before, still the code can only be used if the other data is loaded in seperate files.

AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))

MyData <- merge(MyData, Chelseainfo)

@@

saveWidget(z, file="m.html" )

mapshot(z, url = paste0(getwd(), "/map.html"))
```

>>>>

#AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))

MyData <- Chelseainfo %>%
  select(LSOA_CODE, LowUsePerc, WD16NM)%>%
  merge(MyData, .)

@@

#saveWidget(z, file="m.html", selfcontained = FALSE )
setwd("/home/jonno")
mapshot(z, url = paste0(getwd(), "/map.html"))
```

gSimplify
```{r}
test <- gSimplify(MyData,tol= .0001, topologyPreserve = T) %>% 
  SpatialPolygonsDataFrame(.)

library(geojsonio)
states_json <- geojson_json(MyData,geometry = "polygon")

test <- states_json %>% 
  ms_simplify(keep = 0.005,keep_shapes = TRUE, explode = TRUE) %>% # Simplify polygon
  geojson_sp()

plot(test)

m2 <- leaflet(test) %>%
    #addTiles()
    addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = v))

bins <- c(0, 10, 20, 25, 100)
pal <- colorBin("YlOrRd", domain = test$LowUsePerc, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>Low-use  %g &#37",
  test$WD16NM, test$LowUsePerc
) %>% lapply(htmltools::HTML)

z2 <-m2 %>% addPolygons(
  fillColor = ~pal(LowUsePerc),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
    position = "bottomright")
saveWidget(z2, file="mapsimple2.html", selfcontained = FALSE )
mapshot(z2, url = paste0(getwd(), "/mapsimple.html"))
```
